# Homework 1

## Team 9:
- Charlie Madison
- Hrishi Mysore Harishkumar
- Michelle Li
- Qizhuang Huang
- Shaun Pfister
- Rodolfo Lerma

## Description
The data set presented contains information about the unit price of houses in New Taipei City, Taiwan. 

- **age:** The age of the house in years
- **distance:** The distance to the nearest Mass Rapid Transit (MRT) station from the house (in meters)
- **convenience_stores:** The number of convenience stores near the house.
- **unit_price:** The unit price of the house, measured in 10,000 New Taiwan Dollars/Ping (1 Ping = 3.3 m2)


## Question 1:
*Load the data in R and fit a simple linear regression of unit_price onto convenience_stores.*

```{r}
#Loading Libraries
library(tidyverse)
library(ISLR2)
```


```{r}
df <- read.csv("real-estate-valuation-data-set.csv")
glimpse(df)
```

```{r}
head(df, 5)
tail(df, 5)
```
```{r}
#Looking at the data
plot(unit_price ~ convenience_stores, data = df)
```
```{r}
lm_fit <- lm(unit_price ~ convenience_stores, data = df)
plot(unit_price ~ convenience_stores, data = df)
abline(lm_fit, col = "blue", lwd = 3)
```
## Question 2:
*Print the summary of the model in R. In plain English, state the interpretation of the coefficient estimate associated with the predictor convenience_stores.*

```{r}
#Summary of the Regression Model
summary(lm_fit)
```
###Interpretation of the coefficients

```{r}
sprintf(
    "We estimate that when there are no conveinence stores near the house the average price of a house to be $%.2f",lm_fit$coefficients[1] * 10000
)
```

```{r}
sprintf(
    "We estimate that every unit increase in the number of convenience stores near by the home is associated with a $%.2f change in the average median house value",
    lm_fit$coefficients[2] * 10000
)
```

## Question 3:
*Does the model indicate a statistically significant association between convenience_stores and unit_price? Explain.*

## Question 4:
*Create a 99% confidence interval for the coefficient associated with the predictor convenience_stores.*

## Question 5:
*Fit a multiple linear regression of unit_price onto convenience_stores and distance. Evaluate the Variance Inflation Factors for this model and state whether you have any concerns regarding collinearity problems between the two predictors.*

## Question 6:
*Print the summary of the model in R. In plain English, state the interpretation of the coefficients associated with the predictors convenience_stores and distance*

## Question 7:
*In plain English, state the interpretation of the results of the F-test for this model.*

## Question 8:
*In plain English, state the interpretation of the coefficient of determination R2 for this model (this can also be found using the summary function).*

## Question 9:
*Create a plot of unit_price vs. convenience_stores and a plot of unit_price vs. distance*

## Question 10:
*Based on these plots, do you believe the multiple linear regression model that we just built is appropriate for these data? Explain.*