# Homework 1

## Team 9:
- Charlie Madison
- Hrishi Mysore Harishkumar
- Michelle Li
- Qizhuang Huang
- Shaun Pfister
- Rodolfo Lerma

## Description
The data set presented contains information about the unit price of houses in New Taipei City, Taiwan. 

- **age:** The age of the house in years
- **distance:** The distance to the nearest Mass Rapid Transit (MRT) station from the house (in meters)
- **convenience_stores:** The number of convenience stores near the house.
- **unit_price:** The unit price of the house, measured in 10,000 New Taiwan Dollars/Ping (1 Ping = 3.3 m2)


## Question 1:
**Load the data in R and fit a simple linear regression of unit_price onto convenience_stores.**

```{r, message = FALSE}
#Loading Libraries
library(tidyverse)
library(car)
library(leaps)
library(msm)
```


```{r}
df <- read.csv("real-estate-valuation-data-set.csv")
glimpse(df)
```

```{r}
head(df, 5)
tail(df, 5)
```
```{r}
#Looking at unit_price vs convenience_stores
plot(unit_price ~ convenience_stores, data = df)
grid(nx = NULL, ny = NULL,
     lty = 2, col = "gray", lwd = 2)
title(main = "Unit Price Vs Convenience Stores ")
```
```{r}
lm_fit <- lm(unit_price ~ convenience_stores, data = df)
plot(unit_price ~ convenience_stores, data = df)
abline(lm_fit, col = "blue", lwd = 3) 
legend("topleft",legend=paste("R2 is", format(summary(lm_fit)$r.squared,digits=3)))
grid(nx = NULL, ny = NULL,
     lty = 2, col = "gray", lwd = 2)
title(main = "Regression Line (Unit Price Vs Convenience Stores)")
```

## Question 2:
**Print the summary of the model in R. In plain English, state the interpretation of the coefficient estimate associated with the predictor convenience_stores.**

```{r}
#Summary of the Regression Model
summary(lm_fit)
```

```{r}
sprintf(
    "We estimate that when there are no convenience stores near the house the average price of the noted house would be $%.2f",lm_fit$coefficients[1] * 10000
)
```

```{r}
sprintf(
    "We estimate that every unit increase in the number of convenience stores near the home is associated with a $%.2f change in the average median house value",
    lm_fit$coefficients[2] * 10000
)
```

## Question 3:
**Does the model indicate a statistically significant association between convenience_stores and unit_price? Explain.**

```{r}
summary(lm_fit)$coefficients
```

```{r}
sprintf(
    "Looking at the Pvalue (%e) for the beta_1 *convenience_stores* coefficient we can see that there is a statistical association between the number of convenience stores and the price of the home in this data set.",
    summary(lm_fit)$coefficients[2,4]
)
```
```{r}
sprintf(
    "Also the Rsquared value is pointing in the same direction as the number of convenience stores near the house can expplain %.2f percent of the variation in the data.",
    summary(lm_fit)$r.squared*100
)
```

## Question 4:
**Create a 99% confidence interval for the coefficient associated with the predictor convenience_stores.**

```{r}
# Confidence intervals.
confint(lm_fit, level = 0.99)
```

## Question 5:
**Fit a multiple linear regression of unit_price onto convenience_stores and distance. Evaluate the Variance Inflation Factors for this model and state whether you have any concerns regarding collinearity problems between the two predictors.**
 
```{r}
#Multi Linear Regression Model
lm_fit_mult <- lm(unit_price ~ convenience_stores + distance, data = df)
```

```{r}
# Collinarity.
vif(lm_fit_mult)
```

Based on the noted values above (and both being smaller than 5) there is no concern on collinearity between these 2 predictors:
- **distance:** The distance to the nearest Mass Rapid Transit (MRT) station from the house (in meters)
- **convenience_stores:** The number of convenience stores near the house.

## Question 6:
**Print the summary of the model in R. In plain English, state the interpretation of the coefficients associated with the predictors convenience_stores and distance.**

```{r}
summary(lm_fit_mult)
```

```{r}
sprintf(
    "We estimate that every unit increase in the number of convenience stores near the home is associated with a $%.2f change in the average median house value",
    lm_fit_mult$coefficients[2] * 10000
)
```

```{r}
sprintf(
    "We estimate that every unit increase in the number of convenience stores near the home is associated with a $%.2f change in the average median house value",
    lm_fit_mult$coefficients[2] * 10000
)
```

## Question 7:
**In plain English, state the interpretation of the results of the F-test for this model.**

```{r}
summary(lm_fit_mult)$fstatistic
```
The noted F-Test is telling us along with its p-value that the model that we have which includes 2 predictors (convenience_stores & distance) is better than a model with only the interceptor and non of the other variables.

## Question 8:
**In plain English, state the interpretation of the coefficient of determination R2 for this model (this can also be found using the summary function).**

```{r}
# between Y and Y_hat in multiple linear regression.
cor(df$unit_price , fitted(lm_fit_mult))^2
```

## Question 9:
**Create a plot of unit_price vs. convenience_stores and a plot of unit_price vs. distance**

```{r}
#Looking at unit_price vs convenience_stores
plot(unit_price ~ convenience_stores, data = df)
abline(lm_fit, col = "purple", lwd = 3)
grid(nx = NULL, ny = NULL,
     lty = 2, col = "gray", lwd = 2)
title(main = "Unit Price Vs Convenience Stores ")
```

```{r}
#Looking at unit_price vs convenience_stores
lm_fit_1 <- lm(unit_price ~ distance, data = df)
lm_fit_2 <- lm(unit_price ~ distance +  I(distance^2), data = df)
plot(unit_price ~ distance, data = df)
abline(lm_fit_1, col = "purple", lwd = 3)
pred_points <- seq(0, 7000, by = 100)
lines(
    pred_points,
    predict(lm_fit_2, data.frame(distance = pred_points)),
    col = "blue",
    lwd = 3
)
grid(nx = NULL, ny = NULL,
     lty = 2, col = "gray", lwd = 2)
title(main = "Unit Price Vs Distance ")
```

## Question 10:
**Based on these plots, do you believe the multiple linear regression model that we just built is appropriate for these data? Explain.**

No, it is possible to see that for the variable *distance* a quadratic representation of the data in the regression might be better to capture the variation the data and therefore it would be better to make predictions.